### 2020-08-13 3_implementation.tex
Update text for task pruning.

Among distributed task-based systems, there can be a scalability
bottleneck due to enumerating tasks sequentially. PaRSEC and StarPU
allow users to omit tasks that are not directly connected in the
dependence graph. The program is replicated (for efficiency of
analysis), but each task is executed only once. Because the dynamic
checks to see if a task should be executed are not free of cost, we
also provide versions of the PaRSEC and StarPU implementations
(labeled \lstinline{shard} and \lstinline{expl}, respectively)
hand-written to minimize such costs. PaRSEC \lstinline{shard} uses the
DTD mode but manually minimizes dynamic checks. StarPU
\lstinline{expl} uses the MPI integration described above. We see in
Section~\ref{subsec:scalability} that such modifications are needed to
achieve optimal scalability. Regent performs an equivalent
optimization at compile time~\cite{ControlReplication17} that does not
require user intervention and preserves the original, implicitly
parallel programming model of the language.

>>>>

Among distributed task-based systems, there can be a scalability
bottleneck due to enumerating tasks sequentially. PaRSEC and StarPU
allow users to manually prune the task graph, skipping tasks not
mapped for execution onto a given node, plus a ``halo'' consisting of
tasks connected via dependencies to the set of node-local tasks. Because the dynamic
checks to see if a task should be executed are not free of cost, we
also provide versions of the PaRSEC and StarPU implementations
(labeled \lstinline{shard} and \lstinline{expl}, respectively)
hand-written to minimize such costs. PaRSEC \lstinline{shard} uses the
DTD mode but manually minimizes dynamic checks. StarPU
\lstinline{expl} uses the MPI integration described above. We see in
Section~\ref{subsec:scalability} that such modifications are needed to
achieve optimal scalability. Regent performs an equivalent
optimization at compile time~\cite{ControlReplication17} that does not
require user intervention and preserves the original, implicitly
parallel programming model of the language.
